### 2016-06-08 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Updated TC/HRR uncertainty sections of gas burner report

\subsubsection{Thermocouples}
The standard uncertainty in the temperature of the thermocouple wire itself is $\pm$2.2$~^{\circ}$C at $277~^{\circ}$C and increases to $\pm$9.5$~^{\circ}$C at $871~^{\circ}$C as determined by the wire manufacturer~\cite{Omega:2004}. The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty~\cite{Pitts:2003}. Blevins found that the percent error in the measured upper layer temperature for a 1~mm bare-bead thermocouple is bounded by a maximum of 20~\%~\cite{Blevins:1999}. Small diameter thermocouples were used to limit the impact of radiative heating and cooling. The estimated total expanded uncertainty for temperature in these experiments is $\pm$15~\%. ***\textit{Still need to finish reviewing literature about TC uncertainty and add list of components of standard uncertainty along with description about uncertainty estimate.}***

@@

\subsubsection{Heat Release Rate}
A rotary type gas meter was used to measure the volume of propane provided to the gas burners. The manufacturer quantifies the maximum error as $\pm$2~\%~\cite{Romet:2014}. The measurement was used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire. The total expanded uncertainty for the heat release rate obtained from this method was estimated to be $\pm15$~\%. ***\textit{Still need to finish reviewing literature about HRR uncertainty and add description here about calculation and uncertainty estimate.}***

>>>>

\subsubsection{Thermocouples}
The standard uncertainty in the temperature of the thermocouple wire itself is $\pm$2.2$~^{\circ}$C at $277~^{\circ}$C and increases to $\pm$9.5$~^{\circ}$C at $871~^{\circ}$C as determined by the wire manufacturer~\cite{Omega:2004}. The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty~\cite{Pitts:2003}. Blevins found the maximum percent error for the upper layer temperature measured by a 1~mm bare-bead thermocouple to be 20~\%~\cite{Blevins:1999}. Small diameter thermocouples were used during these experiments to limit the impact of radiative heating and cooling. The estimated total expanded uncertainty for temperature in these experiments is $\pm$15~\%.

@@

\subsubsection{Heat Release Rate}
A rotary type gas meter was used to measure the volume of propane provided to the gas burners. The manufacturer quantifies the maximum error as $\pm$2~\%~\cite{Romet:2014}. A volumetric flow rate was calculated from the gas meter measurements and used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire. The total expanded uncertainty for the heat release rate obtained from this method was estimated to be $\pm12$~\%.
